Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-12-02 paper/paper.tex
minor changes

The auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}. Different tools have been developed to check the fairness of AI models\cite{yuan2024ensuring,saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.

@@

As for privacy, on the other hand, it introduces risks of information leakage. Storage of real data may inadvertently reveal sensitive information by data inference attacks. Indefinite retention exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.

@@

The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022}. We first select the important marginals to preserve, measure them by adding Differential Privacy noise, and then generate synthetic data.

@@

To circumvent the complexity explosion, instead, \cite{McKenna_privatePGM,mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.

For the competition, \cite{McKenna_privatePGM,mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset. For example, they manually added the clique (sex,city,income). In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset. Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.

@@

>>>>

Auditing of AI models is an important step in ensuring that these models are fair\cite{ferrara2023fairness}. Different tools have been developed to check the fairness of AI models\cite{yuan2024ensuring,saleiro2018aequitas,bellamy2019ai,bird2020fairlearn}.

@@

As for privacy, on the other hand, it introduces risks of information leakage. Storage of real data may inadvertently reveal sensitive information by data inference attacks. Indefinite retention also exacerbates this issue because the longer the data is stored, the higher the chance of unwanted information disclosure.

@@

The synthesis framework is three-fold, namely, select-measure-generate\cite{McKenna2022,YouTube_Differentially_Private_Synthetic_Data}. We first select the important marginals to preserve, measure them by adding Differential Privacy noise, and then generate synthetic data.

@@

To circumvent the complexity explosion, instead, \cite{mckenna2021winning} devised a technique where the mutual information of all the database attribute pairs is calculated, and then a maximum spanning tree algorithm was run with edge weights being the mutual information to obtain a skeleton spanning-tree-shaped Markov random field.

For the competition, \cite{mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset. For example, they manually added the clique (sex,city,income). In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset. Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.

@@

% TODO: mention model fit time?
